Reproducibility of published meta-analyses on clinical psychological interventions

### 2023-04-21 submission.tex
Revised version

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ,apa7,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{meta-analysis, reproducibility, data sharing, data reusability, research synthesis}
\usepackage{csquotes}
\usepackage{caption}
\captionsetup[table]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
\captionsetup[figure]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Analytical reproducibility and data reusability of published meta-analyses on clinical psychological interventions},
  pdfauthor={Rubén López-Nicolás1, Daniel Lakens2, Jose A. López-López1, Maria Rubio-Aparicio3, Alejandro Sandoval-Lentisco1, Carmen López-Ibáñez1, Desirée Blázquez-Rincón1, \& Julio Sánchez-Meca1},
  pdflang={en-EN},
  pdfkeywords={meta-analysis, reproducibility, data sharing, data reusability, research synthesis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Analytical reproducibility and data reusability of published meta-analyses on clinical psychological interventions}
\author{Rubén López-Nicolás\textsuperscript{1}, Daniel Lakens\textsuperscript{2}, Jose A. López-López\textsuperscript{1}, Maria Rubio-Aparicio\textsuperscript{3}, Alejandro Sandoval-Lentisco\textsuperscript{1}, Carmen López-Ibáñez\textsuperscript{1}, Desirée Blázquez-Rincón\textsuperscript{1}, \& Julio Sánchez-Meca\textsuperscript{1}}
\date{}

\shorttitle{Meta-analyses reproducibility (PRE-PRINT)}

@@

Correspondence concerning this article should be addressed to Rubén López-Nicolás. E-mail: \href{mailto:rlopez@um.es}{\nolinkurl{rlopez@um.es}}

@@

\abstract{%
Meta-analysis is one of the most useful and powerful research approaches, however, this relevance relies on its credibility. In recent years different concerns about the credibility of psychological research have emerged. Analytical reproducibility of scientific results could be considered as the minimal threshold of it. In this study, our purpose was to assess the analytical reproducibility and data reusability of a set of published meta-analyses. From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in psychology used in a previous study, 217 meta-analyses were selected. We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc), or on request. Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 meta-analyses from different sources. Of these, in the first stage 52 showed a discrepancy larger than 5\% in the main results, in 25 of them, this discrepancy was solved with minor adjustments, or correction of coding errors. In the remaining 27, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of some data, or transcription errors. Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data. On the other hand, the implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.
}

@@

Meta-analysis is widely considered as an important approach to evaluate a body of work. Given the ongoing growth in the number of scientific publications (Bornmann et al., 2021), evidence synthesis approaches -such as meta-analysis- are becoming increasingly relevant for a cumulative science. This relevance rests on the credibility of meta-analytic results, which can be threatened by a lack of rigorous application or poor-quality reporting (Gurevitch et al., 2018). Given the importance of meta-analyses for evidence-based practice, these threats to their credibility need to be closely monitored.

In recent years different concerns on the credibility of empirical claims have emerged. Several projects have systematically attempted to assess the replicability and reproducibility of published scientific results (e.g., Artner et al. (2020); Errington et al. (2021); Open Science Collaboration (2015)). Those initiatives showed many failures to replicate or reproduce the published results. In this context, the empirical assessment of scientific published results credibility has become a major task for the scientific community.

There are different approaches to the empirical assessment of scientific credibility. Reproducibility refers to the attempt to obtain the same results as in the original publication, using the same data and the same analytical procedure. Robustness refers to the assessment of the sensitivity of the originally published results and conclusions to variations in the original analytical strategy using the same data. Replicability is a core principle of the scientific method and refers to the fact that the same scientific evidence should be observed when independent researchers try to answer the same research question from the same approach at different moments using different data. In other words, obtaining the same results, using different data and answering the same question (National Academies of Sciences, Engineering, and Medicine, 2019; Nosek et al., 2022). In this project, we focus on the reproducibility of meta-analyses.

The reproducibility of all published scientific results could be considered as the minimal threshold of scientific credibility (Hardwicke et al., 2021). Different approaches can be adopted for the empirical assessment of reproducibility. For example Nosek et al. (2022) make the distinction between process reproducibility and outcome reproducibility. Following this framework, a process reproducibility assessment could be carried out by reviewing the availability of the materials, data, and precise details of the analytical strategy in the report that are required to proceed with the reproduction attempt. An outcome reproducibility assessment can be carried out when the required elements are retrievable by actually reproducing the analyses. It is worth noting that the difficulty of performing an outcome reproducibility assessment depends on which analytical information is available. The availability of the original analysis code (i.e., the original computational instructions in a programming language) facilitates reproducibility analysis by enabling simply re-running the code on the data. Regrettably, the analysis code is currently seldom available (Hardwicke et al., 2022, 2020; López-Nicolás et al., 2022). When only a verbal summary of the performed analyses is available in the research report (which is the most common scenario in practice), the original analysis needs to be reconstructed. The challenges and implications of failed reproductions in both cases may be of a different nature.

Several reproducibility analyses of meta-analyses have been performed in recent years. For example, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability (López-Nicolás et al., 2022; Polanin et al., 2020). Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies (Gøtzsche et al., 2007; Maassen et al., 2020; Tendal et al., 2009) possibly due to lack of details on how primary effect sizes were selected and computed. In these outcome reproducibility studies, the main task entails reconstructing the original data by retrieving them from the source, namely the included primary studies. Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to select the primary outcomes and how to deal with possible dependency, and the computation of (standardized) effect sizes. Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these, as well as a summary of the required elements to be able to reproduce each stage.

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth, height=\textheight]{results/Figure 1.png}

@@

\label{fig:figs1}
\end{center}
\end{figure*}

Reproducibility analysis typically uses the original data available from the original authors (e.g., Artner et al., 2020; Hardwicke et al., 2021, 2018). This puts the focus of the assessment at factors such as the reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc. Although data availability seems to have improved in the last years (Hardwicke et al., 2018; Tedersoo et al., 2021; Wallach et al., 2018), systematic reviews and meta-analyses appear to be a special case. Typically, the data collected for a meta-analysis is study-level summary data extracted from published primary studies which is commonly reported in the paper through tables or forest plots. This may lead to the idea that common data sharing practices do not apply to meta-analysis. For example, Page et al. (2022) analysed the content of data availability statements from a set of meta-analyses published in 2020. Only 31\% included a data availability statement and only 13\% of these included a link to access the data openly, with 23\% stating that all relevant data are available in the paper itself, 10\% stating that data sharing is not applicable as no datasets were generated, 8\% stating that data sharing is not applicable as the data is drawn from already published literature, and 42\% stating that data were available upon request. It is surprising that, even just considering meta-analyses that included a data availability statement, the authors of these meta-analysis assume that such practices do not apply to meta-analyses or that the data in the article itself is sufficient.

@@

Previous research has revealed that there is room for improvement at different stages of the meta-analytic process pipeline. In this study our purpose is twofold. First, we broadened previous process reproducibility assessments by considering data availability on request and by contacting original authors to request required information to reproduce the meta-analysis. Second, we verified the outcome reproducibility of the meta-analyses that were process-reproducible using the available data. Where previous work focussed on the reproducibility of primary effect sizes, we explored meta-analysis outcome reproducibility using the primary effects sizes already coded by the original authors.

@@

In previous research we identified a pool of 664 meta-analytic reports on clinical psychological interventions published between 2000 and 2020 through a systematic electronic search (López-Nicolás et al., 2022). Of this pool, 100 were randomly selected using a random number generator between 1 and the total number of meta-analyses identified. The full search strategies and a summary of the screening process are available at: \url{https://osf.io/z5vrn/}, and the workflow of the random selection process is available at: \url{https://osf.io/cp293/}.
From these 100 articles, each independent reported meta-analysis with at least 10 primary studies was selected. In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, which was the case for 29 of the articles included in this report. Our unit of analysis was each independent meta-analysis selected under these criteria. A total of 217 independent meta-analyses were selected.

@@

The availability of necessary primary data was checked. First, we searched for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal. Second, we looked for available data through tables or forest plots in the meta-analytic report itself, or in supplementary material. In these cases, the primary data had to be manually re-coded to reuse it. Finally, if the primary data of a meta-analysis were not directly available after the previous steps, we attempted to obtain the data through a request to the corresponding author identified in the associated paper. We sent an initial request in June 2021 and, if there was no reply, a subsequent reminder in October 2021. This reminder was sent to a more recent alternative email address if we were able to find one. If we were unable to obtain the data through the email request, the associated meta-analysis was labelled as not process reproducible.

In order to be able to reproduce meta-analyses, primary effects and their associated standard errors are required. These are generally computed from primary statistics retrieved from the primary studies such as means, standard deviations or sample sizes. We attempted to retrieve the least processed data possible. First, we sought for the primary statistics, recovered in 26\% of the cases. Second, we sought for the primary effects and their standard errors (or, alternatively, the sampling variances), recovered in 5\% of the cases. Finally, we sought for the primary effects and their confidential limits, recovered in 69\% of the cases, from which the standard errors were approximated as follows:

@@

with \(se_i\) being the standard error of the ith effect size, \(UB_i\) and \(LB_i\) the upper and lower confidence limits of confidence interval for the ith effect size, and \(z_{\alpha/2}\) the \(1 - z_{\alpha/2}\) quantile of the standard normal distribution (usually, \(z_{\alpha/2} = 1.96\) assuming a two-sided 95\% confidence interval).

@@

To proceed with reproducibility attempts of the meta-analyses that were labelled as process reproducible, we first looked for the availability of the original analysis script. When it was available, analytical reproducibility was checked by rerunning the original script on the associated primary data. In 141 cases (97\%), the analysis script code was not available. In these cases we tried to reconstruct the original analytical scheme using the technical details reported in the paper. Specifically, we collected information on: (a) the meta-analytic model originally assumed; (b) the weighting scheme; (c) the between-studies variance estimator; (d) the method used to compute the confidence interval; and (e) the software used to perform the meta-analysis. If any of these details about the analytical methods were not reported, but the software used was mentioned, we inferred the first four pieces of information from the default settings of the software used. If the software used was not reported, we inferred this information from the default settings of the most used software in the sample, which was \emph{Comprehensive Meta-Analysis}.

@@

Primary-level data and aggregate-level data described above were coded by five members of the group. At a first pilot stage, a random sample of five articles of the total pool was independently coded by the five members and, subsequently, in a series of meetings, disagreements between the coders were resolved by consensus. Next, the initial pool of 100 included articles was split among four coders, 25 articles each. A random sample of 25 articles of the total pool was assigned to the fifth member to carry out independent double-coding, with the goal to examine the reliability of the data collection process. Disagreements were resolved by consensus and by double-checking the original materials.

@@

Analytical reproducibility checks were carried out at different stages. First, through reported analytic details or script code. When the analysis script code was available, computational reproducibility was checked by rerunning the script with the available primary data. In most cases, the analysis script code was not available. Thus, in these cases we coded the analytic details as explained above to fit equivalent meta-analytic models as a function of these details using the available primary data. This analysis scheme was programmed in the R environment (R Core Team, 2022) using the \emph{metafor} package (Viechtbauer, 2010).

@@

Figure 6 summarises the results of the whole process of outcome reproducibility assessment.

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{results/Figure 6.png}

\label{fig:fig6}
\end{center}
\end{figure*}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ,man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{meta-analysis, reproducibility, data sharing, data reusability, research synthesis}
\usepackage{csquotes}
\usepackage{caption}
\captionsetup[table]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
\captionsetup[figure]{textfont={footnotesize, it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Reproducibility of published meta-analyses on clinical psychological interventions},
  pdfauthor={Rubén López-Nicolás1, Daniel Lakens2, Jose A. López-López1, Maria Rubio-Aparicio3, Alejandro Sandoval-Lentisco1, Carmen López-Ibáñez1, Desirée Blázquez-Rincón1, \& Julio Sánchez-Meca1},
  pdflang={en-EN},
  pdfkeywords={meta-analysis, reproducibility, data sharing, data reusability, research synthesis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Reproducibility of published meta-analyses on clinical psychological interventions}
\author{Rubén López-Nicolás\textsuperscript{1}, Daniel Lakens\textsuperscript{2}, Jose A. López-López\textsuperscript{1}, Maria Rubio-Aparicio\textsuperscript{3}, Alejandro Sandoval-Lentisco\textsuperscript{1}, Carmen López-Ibáñez\textsuperscript{1}, Desirée Blázquez-Rincón\textsuperscript{1}, \& Julio Sánchez-Meca\textsuperscript{1}}
\date{}

\shorttitle{Meta-analyses reproducibility}

@@

Correspondence concerning this article should be addressed to Rubén López-Nicolás, Facultad de Psicología, Campus de Espinardo, Universidad de Murcia, edificio n° 31, 30100, Murcia, Spain. E-mail: \href{mailto:rlopez@um.es}{\nolinkurl{rlopez@um.es}}

@@

\abstract{%
Meta-analysis is one of the most useful and powerful research approaches, the relevance of which relies on its credibility. However, in recent years different concerns about the credibility of psychological research have emerged. Reproducibility of scientific results could be considered as the minimal threshold of it. In this study, our purpose was to assess the reproducibility of a sample of published meta-analyses. From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in clinical psychology, 217 meta-analyses were selected. We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc), or requesting original data from authors. Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 \textcolor{blue}{(67\%, 146/217)} meta-analyses. Of these, 52 showed a discrepancy larger than 5\% in the main results in the first stage. \textcolor{blue}{For 10 meta-analyses this discrepancy was solved after fixing a coding error and for 15 of them it was solved with minor adjustment or considered approximately reproduced in a qualitative assessment.} In the remaining 27 meta-analyses\textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of data, or transcription errors. \textcolor{blue}{Nevertheless, the numerical discrepancies produced by these issues were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data. The implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.
}

@@

Meta-analysis is widely considered as an important approach to evaluate a body of work. Given the ongoing growth in the number of scientific publications (Bornmann et al., 2021), evidence synthesis approaches---such as meta-analysis---are becoming increasingly relevant for a cumulative science. This relevance rests on the credibility of meta-analytic results, which can be threatened by a lack of rigorous methodology or poor-quality reporting (Gurevitch et al., 2018). Given the importance of meta-analyses for evidence-based practice, these threats to their credibility need to be closely monitored.

In recent years different concerns on the credibility of empirical claims have emerged. Several projects have systematically attempted to assess the replicability and reproducibility of published scientific results (e.g., Artner et al. (2020); Errington et al. (2021); Open Science Collaboration (2015)). Those initiatives showed many failures to replicate or reproduce the published results. In this context, the empirical assessment of the credibility of published results has become a major task for the scientific community.

There are different approaches to the empirical assessment of scientific credibility. Reproducibility refers to the attempt to obtain the same results as in the original publication, using the same data and the same procedure. Robustness refers to the assessment of the sensitivity of the originally published results and conclusions to variations in the original procedure using the same data. Replicability is a core principle of the scientific method and refers to the fact that the same scientific evidence should be observed when independent researchers try to answer the same research question from the same approach at different moments using different data. In other words, obtaining the same results, using different data and answering the same question (National Academies of Sciences, Engineering, and Medicine, 2019; Nosek et al., 2022). In this project, we focus on the reproducibility of meta-analyses.

The reproducibility of published scientific results could be considered as the minimal threshold of scientific credibility (Hardwicke et al., 2021). Different approaches can be adopted for the empirical assessment of reproducibility. For example Nosek et al. (2022) make the distinction between process reproducibility and outcome reproducibility. Following this framework, a process reproducibility assessment could be carried out by reviewing the availability of the materials, data, or precise details of the analytical strategy in the report that are required to proceed with the reproduction attempt. An outcome reproducibility assessment can be carried out when the required elements are retrievable by actually reproducing the analyses. It is worth noting that the difficulty of performing an outcome reproducibility assessment depends on which analytical information is available. The availability of the original analysis code (i.e., the original computational instructions in a programming language) facilitates reproducibility analysis by enabling simply re-running the code on the data. Regrettably, the analysis code is currently seldom available (Hardwicke et al., 2022, 2020; López-Nicolás et al., 2022). When only a verbal summary of the performed analyses is available in the research report (which is the most common scenario in practice), the original analysis needs to be reconstructed. The challenges and implications of failed reproductions in both cases may be of a different nature.

Several reproducibility analyses of meta-analyses have been performed in recent years. For example, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability (López-Nicolás et al., 2022; Polanin et al., 2020). Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies (Gøtzsche et al., 2007; Maassen et al., 2020; Tendal et al., 2009), possibly due to lack of details on how primary effect sizes were selected and computed. In these outcome reproducibility studies, the main task entails reconstructing the original data by retrieving them from the source, namely the included primary studies. Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to select the primary outcomes and how to deal with possible dependency, and the computation of (standardized) effect sizes. Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these, as well as a summary of the required elements to be able to reproduce each stage. \textcolor{blue}{In this project we focus on the last stage, related to the statistical analysis and quantitative results of the synthesis.}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth, height=\textheight]{results/Figure 1.png}

@@

\label{fig:figs1}
\end{center}
\end{figure}

Reproducibility analysis \textcolor{blue}{of reported quantitative results} typically uses the original data available from the original authors (e.g., Artner et al., 2020; Hardwicke et al., 2021, 2018). This puts the focus of the assessment at factors such as the reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc. Although data availability seems to have improved in the last years (Hardwicke et al., 2018; Tedersoo et al., 2021; Wallach et al., 2018), systematic reviews and meta-analyses appear to be a special case. Typically, the data collected for a meta-analysis is study-level summary data extracted from published primary studies which is commonly reported in the paper through tables or forest plots. This may lead to the idea that common data sharing practices do not apply to meta-analysis. For example, Page et al. (2022) analysed the content of data availability statements from a set of meta-analyses published in 2020. Only 31\% included a data availability statement and only 13\% of these included a link to access the data openly, with 23\% stating that all relevant data are available in the paper itself, 10\% stating that data sharing is not applicable as no datasets were generated, 8\% stating that data sharing is not applicable as the data is drawn from already published literature, and 42\% stating that data were available upon request. It is surprising that, even just considering meta-analyses that included a data availability statement, the authors of these meta-analysis assume that such practices do not apply to meta-analyses, or that the data in the article itself is sufficient.

@@

Previous research has revealed that there is room for improvement at different stages of the meta-analytic process pipeline. In this study our purpose is twofold. First, we broadened previous process reproducibility assessments by considering data availability on request and by contacting original authors to request required information to reproduce the meta-analysis. Second, we verified the outcome reproducibility of the meta-analyses that were process-reproducible using the available data. Where previous work focused on the reproducibility of primary effect sizes, we explored meta-analysis outcome reproducibility using the primary effects sizes already coded by the original authors.

@@

In previous research we identified a pool of 664 meta-analytic reports on clinical psychological interventions published between 2000 and 2020 through a systematic electronic search (López-Nicolás et al., 2022). Of this pool, 100 were randomly selected using a random number generator between 1 and the total number of meta-analyses identified. The full search strategies and a summary of the screening process are available at: \url{https://osf.io/z5vrn/}, and the workflow of the random selection process is available at: \url{https://osf.io/cp293/}. \textcolor{blue}{This sample size was based on our judgement of an acceptable trade-off between informativeness and feasibility.}
From these 100 articles, each independent \textcolor{blue} {pairwise meta-analytic model of aggregate data fitted} on at least 10 primary studies was selected. In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, which was the case for 29 of the articles included in this report. \textcolor{blue}{This criterion was established to focus on the main meta-analyses of each paper, based on the assumption that the search strategies would be designed to maximise the number of primary studies included that were related to the main aims of the paper.}

Our unit of analysis was each independent meta-analysis selected under these criteria. A total of 217 independent meta-analyses were selected.

@@

In order to be able to reproduce meta-analyses of \textcolor{blue}{aggregate data, primary-level}\footnote{By primary-level data we mean aggregate data from included primary studies.} effects sizes and their associated standard errors are required. These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes. We attempted to retrieve the least processed data possible. First, we sought for the statistics \textcolor{blue}{used to compute primary effect sizes (e.g., means, sd)}; second, we sought for the primary effects sizes \textcolor{blue}{already computed} and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows:

@@

with \(se_i\) being the standard error of the ith effect size, \(UB_i\) and \(LB_i\) the upper and lower confidence limits of confidence interval for the ith effect size, and \(z_{\alpha/2}\) the \((1 - {\alpha/2})\%\) percentile of the standard normal distribution (usually, \(z_{\alpha/2} = 1.96\) assuming a two-sided 95\% confidence interval).

\textcolor{blue}{On the other hand, efforts were also made to retrieve the most reusable data possible.} First, we searched for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal. Second, we looked for available data through tables or forest plots in the meta-analytic report itself, or in supplementary material. In these cases, the primary data had to be manually re-coded to reuse it. Finally, if the primary data of a meta-analysis were not directly available after the previous steps, we attempted to obtain the data through a request to the corresponding author identified in the associated paper. We sent an initial request in June 2021 and, if there was no reply, a subsequent reminder in October 2021. This reminder was sent to a more recent alternative email address if we were able to find one. If we were unable to obtain the data through the email request, the associated meta-analysis was labelled as not process reproducible.

@@

To proceed with reproducibility attempts of the meta-analyses that were labelled as process reproducible, we first looked for the availability of the original analysis script. When it was available, reproducibility was checked by rerunning the original script on the associated primary data. When it was not available, we tried to reconstruct the original analytical scheme using the technical details reported in the paper. Specifically, we collected information on: (a) the meta-analytic model originally assumed; (b) the weighting scheme; (c) the between-studies variance estimator; (d) the method used to compute the confidence interval; and (e) the software used to perform the meta-analysis. If any of these details about the analytical methods were not reported, but the software used was mentioned, we inferred the first four pieces of information from the default settings of the software used. If the software used was not reported, we inferred this information from the default settings of the most used software in the sample, which was \emph{Comprehensive Meta-Analysis}. \textcolor{blue}{We designed this procedure to reconstruct the original analytical scheme when the original analysis script was not available instead of trying to request it from the original authors due to: (a) not necessarily all authors of included meta-analyses will actually have an analysis script to share, because many might have used point and click software, and (b) we expected analysis script availability to be very low, and requesting it would have meant sending request for virtually every paper included in our re-analysis.}

@@

\textcolor{blue}{Data collection procedure was carried out by five of the authors.} At a first pilot stage, a random sample of five articles of the total pool was independently coded by the five members and, subsequently, in a series of meetings, disagreements between the coders were resolved by consensus. Next, the initial pool of 100 included articles was split among four coders, 25 articles each. A random sample of 25 articles of the total pool was assigned to the fifth member to carry out independent double-coding, with the goal to examine the reliability of the data collection process. Disagreements were resolved by consensus and by double-checking the original materials. \textcolor{blue}{Details about inter-coder agreement are reported in the Supplementary file.}

@@

Reproducibility checks were carried out at different stages. First, through reported analytic details or script code. When the analysis script code was available, computational reproducibility was checked by rerunning the script with the available primary data. In most cases, the analysis script code was not available. Thus, in these cases we coded the analytic details as explained above to fit equivalent meta-analytic models as a function of these details using the available primary data. This analysis scheme was programmed in the R environment (R Core Team, 2022) using the \emph{metafor} package (Viechtbauer, 2010).

@@
